---
title: "Report of Parameter Estimation of Nonnormal Bifactor Model"
author: "Jujia"
format: html
editor: visual
---

```{r, echo=FALSE, message=FALSE}
#Merge convergence status and parameters
#para.data_file.all <- left_join(para.data.all, files.all ,by="id.rep")
rm(list=ls())
library(tidyr)
library(dplyr)
library(readr)
library(parallel)
library(mirt)
library(stringr)
library(ggplot2)
```

##### Calculate Bias and Rmse

```{r, echo=FALSE}
# Set folder and Input data
main.folder <- "C:/Research/BifactorNonNormality"
data.folder <- paste0(main.folder,"/Data/")
result.folder <- paste0(main.folder,"/Result/")
para.data_file.all <- read.csv(paste0(result.folder,"parameters.csv"),header = TRUE)


#Calculate the delta of each parameters
para.data_file.report <- para.data_file.all%>%
  #filter(!is.na(aG.FlexMIRT))%>%
  mutate(#aG.Flex.delta= as.numeric(aG.FlexMIRT)-as.numeric(aG.real),
         #aS.Flex.delta= as.numeric(aS.FlexMIRT)-as.numeric(aS.real),
         aG.mirt.delta= as.numeric(aG.mirt)-as.numeric(aG.real),
         aS.mirt.delta= as.numeric(aS.mirt)-as.numeric(aS.real),
         c1.mirt.delta= as.numeric(c1.mirt)-as.numeric(c1.real),
         c2.mirt.delta= as.numeric(c2.mirt)-as.numeric(c2.real),
         c3.mirt.delta= as.numeric(c3.mirt)-as.numeric(c3.real)
         )%>%
  filter(!is.na(c1.mirt.delta))

#Arrange skewness according normal to severe
order_Fg <- c("Skewness(G Facotr): Normal", "Skewness(G Facotr): Moderate", "Skewness(G Facotr): Severe")
order_Fs <- c("Skewness(S Facotr): Normal", "Skewness(S Facotr): Moderate", "Skewness(S Facotr): Severe")

#Calculate bias and rmse
para.data_file.summarise <- para.data_file.report%>%
  group_by(Factor, I, N, Fg, Fs)%>%
  summarise(a_GenFactor_bias = round(mean(aG.mirt.delta, na.rm = TRUE),3), 
            a_SpeFactor_bias = round(mean(aS.mirt.delta, na.rm = TRUE),3),
            c1_bias = round(mean(c1.mirt.delta, na.rm = TRUE),3),
            c2_bias = round(mean(c2.mirt.delta, na.rm = TRUE),3),
            c3_bias = round(mean(c3.mirt.delta, na.rm = TRUE),3),
            a_GenFactor_rmse = round(sqrt(mean((aG.mirt.delta)^2, na.rm = TRUE)),3), 
            a_SpeFactor_rmse = round(sqrt(mean((aS.mirt.delta)^2, na.rm = TRUE)),3), 
            c1_rmse = round(sqrt(mean((c1.mirt.delta)^2, na.rm = TRUE)),3), 
            c2_rmse = round(sqrt(mean((c2.mirt.delta)^2, na.rm = TRUE)),3), 
            c3_rmse = round(sqrt(mean((c3.mirt.delta)^2, na.rm = TRUE)),3),
            #Correlation between estimated value (Y) and real value (X)
            a_GenFactor_cor = round(cor(aG.real,aG.mirt)), 
            a_SpeFactor_cor = round(cor(aS.real,aS.mirt)), 
            c1_cor = round(cor(c1.real,c1.mirt)), 
            c2_cor = round(cor(c2.real,c2.mirt)), 
            c3_cor = round(cor(c3.real,c3.mirt))
            )%>%
  mutate(Fg = paste("Skewness(G Facotr):", Fg),
         Fs = paste("Skewness(S Facotr):", Fs))%>%
  mutate(Fg = factor(Fg, levels = order_Fg),
         Fs = factor(Fs, levels = order_Fs)) %>%
  arrange(Fg,Fs) %>%
  mutate(N = as.factor(N))

write.csv(para.data_file.summarise,paste0(result.folder,"summa.csv"))

#summary(para.data_file.summarise)
```

##### Merge all Bias and Rmse into a longer table

```{r, echo=FALSE}

para.data_file.long <- para.data_file.summarise %>%
  pivot_longer(
    cols = a_GenFactor_bias : c3_cor,
    names_to = "metrics_name",
    values_to = "value"
  ) 

summary(para.data_file.long)
```

### 0. Convergence Rate

```{r}
table.all.convergence <- read.csv(paste0(result.folder,"convergence.csv"))
convergence.ana <- table.all.convergence %>%
  mutate(condition=paste0(Factor,"-",I,"-",N))%>%
  group_by(condition)%>%
  summarise(con.ratio = sum(mirt..bfconvergence!=0) / n())

ggplot(data = convergence.ana, aes(x = condition, y = con.ratio)) +
  geom_col() +
  theme(axis.text.x=element_text(angle=-45, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))
```

### 1. Bias

##### Bias of a on General Factor and Specific Factor on Factor=4, I=10

```{r, echo=FALSE}
df <- para.data_file.long %>%
  filter(metrics_name == "a_GenFactor_bias"|
         metrics_name == "a_SpeFactor_bias"
         ) %>%
  filter(Factor == "4", I == "10")


p1 <- ggplot(data = df, aes (x = N, y = value)) +
  geom_point(aes(color = metrics_name, shape = metrics_name),size = 3)+
  scale_color_manual(values = c("#E69F00", "#999999"))+
  scale_shape_manual(values = c(16,18))+
  facet_wrap(Fg~Fs)+
  labs(title = "Bias of 'a' on Factor:4 and Item:10")+
  labs(x = "Sample Size", y = "Bias")+
  theme(axis.text.x=element_text(angle=-45, vjust=0,hjust=0.5),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)

p1
```

##### Bias of a on General Factor and Specific Factor on 1000 Sample Size

```{r, echo=FALSE}
df <- para.data_file.long %>%
  filter(metrics_name == "a_GenFactor_bias"|
         metrics_name == "a_SpeFactor_bias"
         ) %>%
  filter(N == 1000)%>%
  mutate(Factor_I =paste0("Factor:",Factor,"|","Item:",I))
# %>%
#   mutate(Factor_I = factor(Factor_I, levels = c("Factor:2|Item:5","Factor:2|Item:10",
#         "Factor:3|Item:5","Factor:3|Item:10","Factor:4|Item:5","Factor:4|Item:10",)))%>%
#   arrange(Factor_I)


p1 <- ggplot(data = df, aes (x = Factor_I, y = value)) +
  geom_point(aes(color = metrics_name, shape = metrics_name),size = 3)+
  scale_color_manual(values = c("#E69F00", "#999999"))+
  scale_shape_manual(values = c(16,18))+
  facet_wrap(Fg~Fs)+
  labs(title = "Bias of 'a' on Sample Size 1000")+
  labs(x = "Factor and Item", y = "Bias")+
  theme(axis.text.x=element_text(angle=-75, vjust=0,hjust=0.5),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)

p1
```

##### Plot comparison of c1, c2, and c3 on Factor=4, Item=10

```{r, echo=FALSE}
df <- para.data_file.long %>%
  filter(metrics_name == "c1_bias"|
  metrics_name == "c2_bias"|
  metrics_name == "c3_bias"
  )%>%
  filter(Factor == "4", I == "10")

p1 <- ggplot(data = df, aes (x = N, y = value)) +
  geom_point(aes(color = metrics_name, shape = metrics_name),size = 3)+
  scale_color_manual(values = c("#009E73", "#0072B2","#806070"))+
  scale_shape_manual(values = c(16,17,18))+
  facet_wrap(Fg~Fs)+
  labs(title = "Bias of 'c1' 'c2' and 'c3' on Factor:4 and Item:10")+
  labs(x = "Sample Size", y = "Bias")+
  theme(axis.text.x=element_text(angle=-45, vjust=0,hjust=0.5),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)

p1
```

### 2. RMSE

##### Plot rmse of aG and aS, on Factor:4 and Item:10

```{r, echo=FALSE}
df <- para.data_file.long %>%
  filter(metrics_name == "a_GenFactor_rmse"|
         metrics_name == "a_SpeFactor_rmse"
         ) %>%
  filter(Factor == "4", I == "10")


p1 <- ggplot(data = df, aes (x = N, y = value)) +
  geom_point(aes(color = metrics_name, shape = metrics_name),size = 3)+
  scale_color_manual(values = c("#E69F00", "#999999"))+
  scale_shape_manual(values = c(16,18))+
  facet_wrap(Fg~Fs)+
  labs(title = "RMSE of 'a' on Factor:4 and Item:10")+
  labs(x = "Sample Size", y = "RMSE")+
  theme(axis.text.x=element_text(angle=-45, vjust=0,hjust=0.5),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)

p1
```

##### RMSE of a on General Factor and Specific Factor on 1000 Sample Size

```{r, echo=FALSE}
df <- para.data_file.long %>%
  filter(metrics_name == "a_GenFactor_rmse"|
         metrics_name == "a_SpeFactor_rmse"
         ) %>%
  filter(N == 1000)%>%
  mutate(Factor_I =paste0("Factor:",Factor,"|","Item:",I))
# %>%
#   mutate(Factor_I = factor(Factor_I, levels = c("Factor:2|Item:5","Factor:2|Item:10",
#         "Factor:3|Item:5","Factor:3|Item:10","Factor:4|Item:5","Factor:4|Item:10",)))%>%
#   arrange(Factor_I)


p1 <- ggplot(data = df, aes (x = Factor_I, y = value)) +
  geom_point(aes(color = metrics_name, shape = metrics_name),size = 3)+
  scale_color_manual(values = c("#E69F00", "#999999"))+
  scale_shape_manual(values = c(16,18))+
  facet_wrap(Fg~Fs)+
  labs(title = "RMSE of 'a' on 1000 Sample Size")+
  labs(x = "Factor and Item", y = "RMSE")+
  theme(axis.text.x=element_text(angle=-75, vjust=0,hjust=0.5),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)

p1
```

##### Plot comparison of rmse of c1, c2, and c3 on Factor=4, Item=10

```{r, echo=FALSE}
df <- para.data_file.long %>%
  filter(metrics_name == "c1_rmse"|
  metrics_name == "c2_rmse"|
  metrics_name == "c3_rmse"
  )%>%
  filter(Factor == "4", I == "10")

p1 <- ggplot(data = df, aes (x = N, y = value)) +
  geom_point(aes(color = metrics_name, shape = metrics_name),size = 3)+
  scale_color_manual(values = c("#009E73", "#0072B2","#806070"))+
  scale_shape_manual(values = c(16,17,18))+
  facet_wrap(Fg~Fs)+
  labs(title = "RMSE of c1 c2 and c3 on Factor:4 and Item:10")+
  labs(x = "Sample Size", y = "RMSE")+
  theme(axis.text.x=element_text(angle=-45, vjust=0,hjust=0.5),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)

p1
```

### 3. Trends in all conditions

##### Bias of a in General Factor (Trim Outliers \> 3)

```{r, echo=FALSE}
df <- para.data_file.report%>%
  filter(aG.mirt.delta<=3, aS.mirt.delta<=3, c1.mirt.delta<=3, c2.mirt.delta<=3, c3.mirt.delta<=3)%>%
  mutate(N = as.factor(N))

nrow(para.data_file.report)-nrow(df)
print("Deleted")

p1 <- ggplot(data = df, aes (x = interaction(Factor,I), y = aG.mirt.delta, fill = N)) +
  geom_boxplot(color="#555555")+
  facet_wrap(Fg~Fs)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "Bias of a in General Factor (Trim Outliers > 3)")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")+
  scale_fill_manual(values = c("#999999", "#E69F00", "#009E73", "#0072B2"))

p1
```

### 4. IMPACT of all Factors of Conditions

##### ANOVA for aG - a of General Factor

```{r, echo=FALSE}
model.aG <- aov(a_GenFactor_bias ~ Factor*I*N*Fg*Fs, data=para.data_file.summarise)
s.aG <- summary(model.aG)
s.aG[[1]][s.aG[[1]][["Pr(>F)"]] < 0.05 , ]


#model.aG2 <- aov(aG.mirt.bias ~ Factor+I+N+Fg+Fs, data=para.data_file.summarise)
#summary(model.aG2)

#tukey.a.G2 <- TukeyHSD(model.a.G2, "Factor")
#tukey.a.G2
```

##### ANOVA for aS - a of Specific Factor

```{r, echo=FALSE}
model.aS <- aov(a_SpeFactor_bias ~ Factor*I*N*Fg*Fs, data=para.data_file.summarise)
s.aS <- summary(model.aS)
s.aS[[1]][s.aS[[1]][["Pr(>F)"]] < 0.05 , ]
```

##### ANOVA for c1

```{r, echo=FALSE}
model.c1 <- aov(c1_bias ~ Factor*I*N*Fg*Fs, data=para.data_file.summarise)
s.c1 <- summary(model.c1)
s.c1[[1]][s.c1[[1]][["Pr(>F)"]] < 0.05 , ]


#model.c12 <- aov(aS.mirt.bias ~ Factor+I+N+Fg+Fs, data=para.data_file.summarise)
#summary(model.c12)
```

##### ANOVA for c2

```{r, echo=FALSE}
model.c2 <- aov(c2_bias ~ Factor*I*N*Fg*Fs, data=para.data_file.summarise)
s.c2 <- summary(model.c2)
s.c2[[1]][s.c2[[1]][["Pr(>F)"]] < 0.05 , ]


#model.c22 <- aov(c2.mirt.bias ~ Factor+I+N+Fg+Fs, data=para.data_file.summarise)
#summary(model.c22)
```

##### ANOVA for c3

```{r, echo=FALSE}
model.c3 <- aov(c3_bias ~ Factor*I*N*Fg*Fs, data=para.data_file.summarise)
s.c3 <- summary(model.c3)
s.c3[[1]][s.c3[[1]][["Pr(>F)"]] < 0.05 , ]


#model.c32 <- aov(c3.mirt.bias ~ Factor+I+N+Fg+Fs, data=para.data_file.summarise)
#summary(model.c32)
```
