---
title: "Report of Parameter Estimation of Nonnormal Bifactor Model"
author: "Jujia"
format: html
editor: visual
---

```{r, echo=FALSE, message=FALSE}
#Merge convergence status and parameters
#para.data_file.all <- left_join(para.data.all, files.all ,by="id.rep")
rm(list=ls())
library(tidyr)
library(dplyr)
library(readr)
library(parallel)
library(mirt)
library(stringr)
library(ggplot2)
```

##### Calculate Bias and Rmse

```{r, echo=FALSE}
# Set folder and Input data
main.folder <- "C:/BifactorNonNormality"
data.folder <- paste0(main.folder,"/Data/")
result.folder <- paste0(main.folder,"/Result/")
para.data_file.all <- read.csv(paste0(result.folder,"parameters.csv"),header = TRUE)


#Calculate the delta of each parameters
para.data_file.report <- para.data_file.all%>%
  #filter(!is.na(aG.FlexMIRT))%>%
  mutate(#aG.Flex.delta= as.numeric(aG.FlexMIRT)-as.numeric(aG.real),
         #aS.Flex.delta= as.numeric(aS.FlexMIRT)-as.numeric(aS.real),
         aG.mirt.delta= as.numeric(aG.mirt)-as.numeric(aG.real),
         aS.mirt.delta= as.numeric(aS.mirt)-as.numeric(aS.real),
         c1.mirt.delta= as.numeric(c1.mirt)-as.numeric(c1.real),
         c2.mirt.delta= as.numeric(c2.mirt)-as.numeric(c2.real),
         c3.mirt.delta= as.numeric(c3.mirt)-as.numeric(c3.real)
         )%>%
  filter(!is.na(c1.mirt.delta))

#Arrange skewness according normal to severe
order_vec <- c("Normal", "Moderate", "Severe")

#Calculate bias and rmse
para.data_file.summarise <- para.data_file.report%>%
  group_by(Factor, I, N, Fg, Fs)%>%
  summarise(aG.mirt.bias = round(mean(aG.mirt.delta),3), 
            aS.mirt.bias = round(mean(aS.mirt.delta),3),
            c1.mirt.bias = round(mean(c1.mirt.delta),3),
            c2.mirt.bias = round(mean(c2.mirt.delta),3),
            c3.mirt.bias = round(mean(c3.mirt.delta),3),
            aG.mirt.rmse = round(sqrt(mean((aG.mirt.delta)^2)),3), 
            aS.mirt.rmse = round(sqrt(mean((aS.mirt.delta)^2)),3), 
            c1.mirt.rmse = round(sqrt(mean((c1.mirt.delta)^2)),3), 
            c2.mirt.rmse = round(sqrt(mean((c2.mirt.delta)^2)),3), 
            c3.mirt.rmse = round(sqrt(mean((c3.mirt.delta)^2)),3)
            )%>%
  mutate(Fg = factor(Fg, levels = order_vec),
         Fs = factor(Fs, levels = order_vec)) %>%
  arrange(Fg,Fs) %>%
  mutate(N = as.factor(N))

write.csv(para.data_file.summarise,paste0(result.folder,"summa.csv"))

#summary(para.data_file.summarise)
```

##### Merge all Bias and Rmse into a longer table

```{r, echo=FALSE}

para.data_file.long <- para.data_file.summarise %>%
  pivot_longer(
    cols = aG.mirt.bias : c3.mirt.rmse,
    names_to = "metrics_name",
    values_to = "metrics"
  ) 

summary(para.data_file.long)
```

### 0. Convergence Rate

```{r}
table.all.convergence <- read.csv(paste0(result.folder,"convergence.csv"))
convergence.ana <- table.all.convergence %>%
  mutate(condition=paste0(Factor,"-",I,"-",N))%>%
  group_by(condition)%>%
  summarise(con.ratio = sum(mirt..bfconvergence!=0) / n())
convergence.ana
ggplot(data = convergence.ana, aes(x = condition, y = con.ratio)) +
  geom_col() +
  theme(axis.text.x=element_text(angle=-45, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))
```

### 1. Bias

##### Plot comparison of aG and aS, under 1000 sample size

```{r, echo=FALSE}
df_1000 <- para.data_file.long %>%
  filter(N==1000,
  metrics_name == "aG.mirt.bias"|
    metrics_name == "aS.mirt.bias"
  )

p1 <- ggplot(data = df_1000, aes (x = interaction(Fs,Fg), y = metrics, color = metrics_name)) +
  geom_point()+
  scale_color_manual(values = c("#E69F00", "#999999"))+
  facet_wrap(Factor~I)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "Bias of a of General Factor and Specific Factor, under 1000 Sample Size")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")
p1
```

##### Plot comparison of aG and aS, under 250 sample size

```{r, echo=FALSE}
df <- para.data_file.long %>%
  filter(N==250,
  metrics_name == "aG.mirt.bias"|
    metrics_name == "aS.mirt.bias"
  )

p1 <- ggplot(data = df, aes (x = interaction(Fs,Fg), y = metrics, color = metrics_name)) +
  geom_point()+
  scale_color_manual(values = c("#E69F00", "#999999"))+
  facet_wrap(Factor~I)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "Bias of a of General Factor and Specific Factor, under 250 Sample Size")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")
p1
```

##### Plot comparison of c1, c2, and c3 under 1000 sample size

```{r, echo=FALSE}
df_1000 <- para.data_file.long %>%
  filter(N==1000,
  metrics_name == "c1.mirt.bias"|
  metrics_name == "c2.mirt.bias"|
  metrics_name == "c3.mirt.bias"
  )

p1 <- ggplot(data = df_1000, aes (x = interaction(Fs,Fg), y = metrics, color = metrics_name)) +
  geom_point()+
  scale_color_manual(values = c("#009E73", "#0072B2","#806070"))+
  facet_wrap(Factor~I)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "Bias of c1, c2, and c3 under 1000 Sample Size")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")
p1
```

### 2. RMSE

##### Plot rmse of aG and aS, under 1000 sample size

```{r, echo=FALSE}
df_1000 <- para.data_file.long %>%
  filter(N==1000,
  metrics_name == "aG.mirt.rmse"|
    metrics_name == "aS.mirt.rmse"
  )

p1 <- ggplot(data = df_1000, aes (x = interaction(Fs,Fg), y = metrics, color = metrics_name)) +
  geom_point()+
  scale_color_manual(values = c("#E69F00", "#999999"))+
  facet_wrap(Factor~I)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "RMSE of a of General Factor and Specific Factor, under 1000 Sample Size")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")
p1
```

##### Plot rmse of c1, c2, and c3 under 1000 sample size

```{r, echo=FALSE}
df_1000 <- para.data_file.long %>%
  filter(N==1000,
  metrics_name == "c1.mirt.rmse"|
  metrics_name == "c2.mirt.rmse"|
  metrics_name == "c3.mirt.rmse"
  )

p1 <- ggplot(data = df_1000, aes (x = interaction(Fs,Fg), y = metrics, color = metrics_name)) +
  geom_point()+
  scale_color_manual(values = c("#009E73", "#0072B2","#806070"))+
  facet_wrap(Factor~I)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "RMSE of c1, c2, and c3 under 1000 Sample Size")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")
p1
```

### 3. Outliers

```{r, echo=FALSE}
df <- para.data_file.report%>%
  mutate(Fg = factor(Fg, levels = order_vec),
         Fs = factor(Fs, levels = order_vec)) %>%
  arrange(Fg,Fs) %>%
  mutate(N = as.factor(N))


p1 <- ggplot(data = df, aes (x = interaction(Fs,Fg), y = aS.mirt.delta, fill = N)) +
  geom_boxplot(color="#555555")+
  facet_wrap(I~Factor)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "Bias of all Parameters")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")+
  scale_fill_manual(values = c("#999999", "#E69F00", "#009E73", "#0072B2"))

p1
```

### 4. Trends in all conditions

##### Bias of a in General Factor (Trim Outliers \> 3)

```{r, echo=FALSE}
df <- para.data_file.report%>%
  filter(aG.mirt<=3,aS.mirt<=3, c3.mirt<=3,c2.mirt<=3,c1.mirt<=3)%>%
  mutate(Fg = factor(Fg, levels = order_vec),
         Fs = factor(Fs, levels = order_vec)) %>%
  arrange(Fg,Fs) %>%
  mutate(N = as.factor(N))

nrow(para.data_file.report)-nrow(df)
print("Deleted")

p1 <- ggplot(data = df, aes (x = interaction(Fs,Fg), y = aG.mirt.delta, fill = N)) +
  geom_boxplot(color="#555555")+
  facet_wrap(I~Factor)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "Bias of a in General Factor (Trim Outliers > 3)")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")+
  scale_fill_manual(values = c("#999999", "#E69F00", "#009E73", "#0072B2"))

p1
```

##### Bias of a in Specific Factor (Trim Outliers \> 1.5)

```{r, echo=FALSE}
df <- para.data_file.report%>%
  filter(aG.mirt<=5,aS.mirt<=5, c3.mirt<=5,c2.mirt<=5,c1.mirt<=5)%>%
  mutate(Fg = factor(Fg, levels = order_vec),
         Fs = factor(Fs, levels = order_vec)) %>%
  arrange(Fg,Fs) %>%
  mutate(N = as.factor(N))

nrow(para.data_file.report)-nrow(df)
print("Deleted")

p1 <- ggplot(data = df, aes (x = interaction(Fs,Fg), y = aS.mirt.delta, fill = N)) +
  geom_boxplot(color="#555555")+
  facet_wrap(I~Factor)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "Bias of a in Specific Factor (Trim Outliers > 1.5)")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")+
  scale_fill_manual(values = c("#999999", "#E69F00", "#009E73", "#0072B2"))

p1
```

### 5. IMPACT of all conditions

##### ANOVA for aG - a of General Factor

```{r, echo=FALSE}
model.aG <- aov(aG.mirt.bias ~ Factor*I*N*Fg*Fs, data=para.data_file.summarise)
s.aG <- summary(model.aG)
s.aG[[1]][s.aG[[1]][["Pr(>F)"]] < 0.05 , ]


#model.aG2 <- aov(aG.mirt.bias ~ Factor+I+N+Fg+Fs, data=para.data_file.summarise)
#summary(model.aG2)

#tukey.a.G2 <- TukeyHSD(model.a.G2, "Factor")
#tukey.a.G2
```

##### ANOVA for aS - a of Specific Factor

```{r, echo=FALSE}
model.aS <- aov(aS.mirt.bias ~ Factor*I*N*Fg*Fs, data=para.data_file.summarise)
s.aS <- summary(model.aS)
s.aS[[1]][s.aS[[1]][["Pr(>F)"]] < 0.05 , ]


#model.aS2 <- aov(aS.mirt.bias ~ Factor+I+N+Fg+Fs, data=para.data_file.summarise)
#summary(model.aS2)
```

##### ANOVA for c1

```{r, echo=FALSE}
model.c1 <- aov(c1.mirt.bias ~ Factor*I*N*Fg*Fs, data=para.data_file.summarise)
s.c1 <- summary(model.c1)
s.c1[[1]][s.c1[[1]][["Pr(>F)"]] < 0.05 , ]


#model.c12 <- aov(aS.mirt.bias ~ Factor+I+N+Fg+Fs, data=para.data_file.summarise)
#summary(model.c12)
```

##### ANOVA for c2

```{r, echo=FALSE}
model.c2 <- aov(c2.mirt.bias ~ Factor*I*N*Fg*Fs, data=para.data_file.summarise)
s.c2 <- summary(model.c2)
s.c2[[1]][s.c2[[1]][["Pr(>F)"]] < 0.05 , ]


#model.c22 <- aov(c2.mirt.bias ~ Factor+I+N+Fg+Fs, data=para.data_file.summarise)
#summary(model.c22)
```

##### ANOVA for c3

```{r, echo=FALSE}
model.c3 <- aov(c3.mirt.bias ~ Factor*I*N*Fg*Fs, data=para.data_file.summarise)
s.c3 <- summary(model.c3)
s.c3[[1]][s.c3[[1]][["Pr(>F)"]] < 0.05 , ]


#model.c32 <- aov(c3.mirt.bias ~ Factor+I+N+Fg+Fs, data=para.data_file.summarise)
#summary(model.c32)
```
