---
title: "Report of Theta of Nonnormal Bifactor Model"
author: "Jujia"
format: html
editor: visual
---

```{r, echo=FALSE, message=FALSE}
#Merge convergence status and parameters
#para.theta.all <- left_join(para.data.all, files.all ,by="id.rep")
rm(list=ls())
library(tidyr)
library(dplyr)
library(readr)
library(parallel)
library(mirt)
library(stringr)
library(ggplot2)
```

##### Calculate Bias and Rmse

######Infinite Number in MAP:

```{r, echo=FALSE, warning=FALSE}
# Set folder and Input data
main.folder <- "C:/Research/BifactorNonNormality"
data.folder <- paste0(main.folder,"/Data/")
result.folder <- paste0(main.folder,"/Result/")
para.theta.all <- read.csv(paste0(result.folder,"thetas.csv"),header = TRUE)


#Calculate the delta of each parameters
theta.mirt.MAP.report <- para.theta.all%>%
  filter(!is.infinite(thetaG.mirt.map))%>%
  filter(!is.infinite(thetaS.avg.mirt.map))%>%          
  mutate(
    Factor = paste0("Factor: ",Factor),
    I = paste0("Item: ",I),
    thetaG.mirt.map.delta = as.numeric(thetaG.mirt.map) - as.numeric(thetaG.real),
    thetaS.mirt.map.delta = as.numeric(thetaS.avg.mirt.map) - as.numeric(thetaS.avg.real)
  )

nrow(para.theta.all)-nrow(theta.mirt.MAP.report)
```

######Infinite Number in ML

```{r, echo=FALSE, warning=FALSE}
theta.mirt.ML.report <- para.theta.all%>%
  filter(!is.infinite(thetaG.mirt.ml))%>%
  filter(!is.infinite(thetaS.avg.mirt.ml))%>%          
  mutate(
    Factor = paste0("Factor: ",Factor),
    I = paste0("Item: ",I),
    thetaG.mirt.ml.delta = as.numeric(thetaG.mirt.ml) - as.numeric(thetaG.real),
    thetaS.mirt.ml.delta = as.numeric(thetaS.avg.mirt.ml) - as.numeric(thetaS.avg.real)
  )
#"Infinite Number in ML:"
nrow(para.theta.all)-nrow(theta.mirt.ML.report)



#Arrange skewness according normal to severe
order_vec <- c("Normal", "Moderate", "Severe")

#Calculate bias and rmse of MAP
theta.mirt.MAP.summarise <- theta.mirt.MAP.report%>%
  group_by(Factor, I, N, Fg, Fs)%>%
  summarise(
    thetaG.mirt.map.bias = round(mean(thetaG.mirt.map.delta),3),
    thetaS.mirt.map.bias = round(mean(thetaS.mirt.map.delta),3),
    thetaG.mirt.map.rmse = round(sqrt(mean((thetaG.mirt.map.delta)^2)),3),
    thetaS.mirt.map.rmse = round(sqrt(mean((thetaS.mirt.map.delta)^2)),3),
    thetaG.mirt.map.cor = cor(thetaG.real, thetaG.mirt.map),
    thetaS.mirt.map.cor = cor(thetaS.avg.real, thetaS.avg.mirt.map)
            )%>%
  mutate(Fg = factor(Fg, levels = order_vec),
         Fs = factor(Fs, levels = order_vec)) %>%
  arrange(Fg,Fs) %>%
  mutate(N = as.factor(N))

#Calculate bias and rmse of ML
theta.mirt.ML.summarise <- theta.mirt.ML.report%>%
  group_by(Factor, I, N, Fg, Fs)%>%
  summarise(
    thetaG.mirt.ml.bias = round(mean(thetaG.mirt.ml.delta),3),
    thetaS.mirt.ml.bias = round(mean(thetaS.mirt.ml.delta),3),    
    thetaG.mirt.ml.rmse = round(sqrt(mean((thetaG.mirt.ml.delta)^2)),3),
    thetaS.mirt.ml.rmse = round(sqrt(mean((thetaS.mirt.ml.delta)^2)),3),
    thetaG.mirt.ml.cor = cor(thetaG.real, thetaG.mirt.ml),
    thetaS.mirt.ml.cor = cor(thetaS.avg.real, thetaS.avg.mirt.ml)
            )%>%
  mutate(Fg = factor(Fg, levels = order_vec),
         Fs = factor(Fs, levels = order_vec)) %>%
  arrange(Fg,Fs) %>%
  mutate(N = as.factor(N))


#write.csv(theta.mirt.MAP.summarise,paste0(result.folder,"summa_theta_MAP.csv"))
#write.csv(theta.mirt.ML.summarise,paste0(result.folder,"summa_theta_ML.csv"))
#summary(para.theta.summarise)
```

##### Merge all Bias and Rmse into a longer table

```{r, echo=FALSE}
theta.mirt.MAP.long <- theta.mirt.MAP.summarise %>%
  pivot_longer(
    cols = thetaG.mirt.map.bias : thetaS.mirt.map.cor,
    names_to = "metrics_name",
    values_to = "value"
  ) 



theta.mirt.ML.long <- theta.mirt.ML.summarise %>%
  pivot_longer(
    cols = thetaG.mirt.ml.bias : thetaS.mirt.ml.cor,
    names_to = "metrics_name",
    values_to = "value"
  ) 

theta.mirt.long <- rbind(theta.mirt.MAP.long, theta.mirt.ML.long)

```

### 1. Bias of Theta

##### Plot comparison MAP and ML : thetaG and thetaS, under 1000 sample size

```{r, echo=FALSE}
df_1000 <- theta.mirt.long %>%
  filter(N==1000,
    metrics_name == "thetaG.mirt.map.bias"|
    metrics_name == "thetaS.mirt.map.bias"|
    metrics_name == "thetaG.mirt.ml.bias"|
    metrics_name == "thetaS.mirt.ml.bias"
  )%>%
  mutate(metrics_name = factor(metrics_name, levels = c("thetaG.mirt.map.bias",
              "thetaS.mirt.map.bias","thetaG.mirt.ml.bias","thetaS.mirt.ml.bias")))%>%
  arrange(metrics_name)

p1 <- ggplot(data = df_1000, aes (x = interaction(Fs,Fg), y = value, color = metrics_name)) +
  geom_point()+
  scale_color_manual(values = c("#1cb061", "#97e6bb", "#e66c20", "#e6a781"))+
  facet_wrap(I~Factor)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "Bias of THETA under 1000 Sample Size")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")
p1
```

##### MAP: thetaG and thetaS, under 1000 sample size

```{r, echo=FALSE}
df_1000 <- theta.mirt.long %>%
  filter(N==1000,
    metrics_name == "thetaG.mirt.map.bias"|
    metrics_name == "thetaS.mirt.map.bias"
  )%>%
  mutate(metrics_name = factor(metrics_name, levels = c("thetaG.mirt.map.bias",
              "thetaS.mirt.map.bias")))%>%
  arrange(metrics_name)

p1 <- ggplot(data = df_1000, aes (x = interaction(Fs,Fg), y = value, color = metrics_name)) +
  geom_point()+
  scale_color_manual(values = c("#1cb061", "#97e6bb", "#e66c20", "#e6a781"))+
  facet_wrap(I~Factor)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "Bias of THETA under 250 Sample Size")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")
p1
```

### 2. RMSE

##### Plot comparison MAP and ML : rmse of thetaG and thetaS, under 1000 sample size

```{r, echo=FALSE}
df_1000 <- theta.mirt.long %>%
  filter(N==1000,
    metrics_name == "thetaG.mirt.map.rmse"|
    metrics_name == "thetaS.mirt.map.rmse"|
    metrics_name == "thetaG.mirt.ml.rmse"|
    metrics_name == "thetaS.mirt.ml.rmse"
  )%>%
  mutate(metrics_name = factor(metrics_name, levels = c("thetaG.mirt.map.rmse",
              "thetaS.mirt.map.rmse","thetaG.mirt.ml.rmse","thetaS.mirt.ml.rmse")))%>%
  arrange(metrics_name)

p1 <- ggplot(data = df_1000, aes (x = interaction(Fs,Fg), y = value, color = metrics_name)) +
  geom_point()+
  scale_color_manual(values = c("#1cb061", "#97e6bb", "#e66c20", "#e6a781"))+
  facet_wrap(I~Factor)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "RMSE of THETA under 1000 Sample Size")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")
p1
```

##### MAP : rmse of thetaG and thetaS, under 1000 sample size

```{r, echo=FALSE}
df_1000 <- theta.mirt.long %>%
  filter(N==1000,
    metrics_name == "thetaG.mirt.map.rmse"|
    metrics_name == "thetaS.mirt.map.rmse"
  )%>%
  mutate(metrics_name = factor(metrics_name, levels = c("thetaG.mirt.map.rmse",
              "thetaS.mirt.map.rmse")))%>%
  arrange(metrics_name)

p1 <- ggplot(data = df_1000, aes (x = interaction(Fs,Fg), y = value, color = metrics_name)) +
  geom_point()+
  scale_color_manual(values = c("#1cb061", "#97e6bb", "#e66c20", "#e6a781"))+
  facet_wrap(I~Factor)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "MAP: RMSE of THETA under 1000 Sample Size")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")
p1
```

### 3. Correlation of Theta

##### Correlation of thetaG and thetaS, under 1000 sample size

```{r, echo=FALSE}
df_1000 <- theta.mirt.long %>%
  filter(N==1000,
    metrics_name == "thetaG.mirt.map.cor"|
    metrics_name == "thetaS.mirt.map.cor"|
    metrics_name == "thetaG.mirt.ml.cor"|
    metrics_name == "thetaS.mirt.ml.cor"
  )%>%
  mutate(metrics_name = factor(metrics_name, levels = c("thetaG.mirt.map.cor",
              "thetaS.mirt.map.cor","thetaG.mirt.ml.cor","thetaS.mirt.ml.cor")))%>%
  arrange(metrics_name)

p1 <- ggplot(data = df_1000, aes (x = interaction(Fs,Fg), y = value, color = metrics_name)) +
  geom_point()+
  scale_color_manual(values = c("#1cb061", "#97e6bb", "#e66c20", "#e6a781"))+
  facet_wrap(I~Factor)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "Correlation of THETA under 1000 Sample Size")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")
p1
```

### 4. Outliers

```{r, echo=FALSE}
df <- theta.mirt.MAP.report%>%
  mutate(Fg = factor(Fg, levels = order_vec),
         Fs = factor(Fs, levels = order_vec)) %>%
  arrange(Fg,Fs) %>%
  mutate(N = as.factor(N))


p1 <- ggplot(data = df, aes (x = interaction(Fs,Fg), y = thetaG.mirt.map.delta, fill = N)) +
  geom_boxplot(color="#555555")+
  facet_wrap(I~Factor)+
  #facet_grid(cols=vars(smoke, black))+
  labs(title = "Bias of all Thetas")+
  theme(axis.text.x=element_text(angle=-90, vjust=0.4,hjust=1.2),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = c(3.5,6.5) , linetype = "dashed")+
  scale_fill_manual(values = c("#999999", "#E69F00", "#009E73", "#0072B2"))

p1
```

### 5. IMPACT of all conditions

##### ANOVA for thetaG - theta on General Factor using MAP

```{r, echo=FALSE}
model.thetaG <- aov(thetaG.mirt.map.bias ~ Factor*I*N*Fg*Fs, data=theta.mirt.MAP.summarise)
s.thetaG <- summary(model.thetaG, digits = 4, signif.stars = TRUE)
s.thetaG
#model.aG2 <- aov(aG.mirt.bias ~ Factor+I+N+Fg+Fs, data=para.theta.summarise)
#summary(model.aG2)

#tukey.a.G2 <- TukeyHSD(model.a.G2, "Factor")
#tukey.a.G2
```

##### ANOVA for thetaS - theta on Specific Factor using MAP

```{r, echo=FALSE}
model.thetaS <- aov(thetaS.mirt.map.bias ~ Factor*I*N*Fg*Fs, data=theta.mirt.MAP.summarise)
s.thetaS <- summary(model.thetaS,  digits = 4, signif.stars = TRUE)
s.thetaS
```

##### ANOVA for thetaG - theta on General Factor using ML

```{r, echo=FALSE}
model.thetaG.ml <- aov(thetaG.mirt.ml.bias ~ Factor*I*N*Fg*Fs, data=theta.mirt.ML.summarise)
s.thetaG.ml <- summary(model.thetaG.ml)
#s.thetaG.ml[[1]][s.thetaG.ml[[1]][["Pr(>F)"]] < 0.05, ]
s.thetaG.ml
```

##### ANOVA for thetaS - theta on Specific Factor using ML

```{r, echo=FALSE}
model.thetaS.ml <- aov(thetaS.mirt.ml.bias ~ Factor*I*N*Fg*Fs, data=theta.mirt.ML.summarise)
s.thetaS.ml <- summary(model.thetaS.ml, digits = 4, signif.stars = TRUE)
s.thetaS.ml
```

##### ANOVA for correlation of thetaG using MAP

```{r, echo=FALSE}
model.thetaG.map.cor <- aov(thetaG.mirt.map.cor ~ Factor*I*N*Fg*Fs, data=theta.mirt.MAP.summarise)
s.thetaG.cor <- summary(model.thetaG.map.cor, digits = 4, signif.stars = TRUE)
s.thetaG.cor 
```

##### ANOVA for correlation of thetaG using MAP

```{r, echo=FALSE}
model.thetaS.map.cor <- aov(thetaS.mirt.map.cor ~ Factor*I*N*Fg*Fs, data=theta.mirt.MAP.summarise)
s.thetaS.cor <- summary(model.thetaS.map.cor, digits = 4, signif.stars = TRUE)
s.thetaS.cor
```
